Author disambiguation of large-scale semi-labeled collections of scientific articles

### 2015-08-20 paper.tex
added data
save

In this
framework, author disambiguation can be stated as the problem of
finding a partition ${\cal C} = \{ c_0, ..., c_{M-1} \}$ of ${\cal S}$ such
that ${\cal S} = \cup_{i=0}^{M-1} c_i$, $c_i \cap c_j = \phi$ for all $i \neq
j$, and where subsets $c_i$, or clusters, each corresponds to the set of all
signatures belonging to the same individual $a_i$. Alternatively, the set
${\cal A}$ may remain (possibly partially) unknown, such that author
disambiguation boils down to finding a partition ${\cal C}$ where
subsets $c_i$  each corresponds to the set of all signatures from a same
individual. Finally, in the case of partially annotated databases as studied in
this work, the setting extends with the partial knowledge of pairs $(a, s) \in
{\cal A} \times {\cal S}$, each indicating that signature $s$ is known with high confidence
to belong to individual $a$.

@@

\glnote{I am not sure we need an explicit algorithm, but adding a few examples would help.}

@@

% balancing difficult and easy cases
% sampling pairs from block only

\subsection{Semi-supervised clustering}
\label{methods:clustering}
\glnote{By Gilles}

>>>>

In this
framework, author disambiguation can be stated as the problem of
finding a partition ${\cal C} = \{ c_0, ..., c_{M-1} \}$ of ${\cal S}$ such
that ${\cal S} = \cup_{i=0}^{M-1} c_i$, $c_i \cap c_j = \phi$ for all $i \neq
j$, and where subsets $c_i$, or clusters, each corresponds to the set of all
signatures belonging to the same individual $a_i$. Alternatively, the set
${\cal A}$ may remain (possibly partially) unknown, such that author
disambiguation boils down to finding a partition ${\cal C}$ where
subsets $c_i$  each corresponds to the set of all signatures from a same
individual. Finally, in the case of partially annotated databases as studied in
this work, the setting extends with the partial knowledge of pairs ${\cal C} = \{ (a, s) \in
{\cal A} \times {\cal S} \}$, each indicating that signature $s$ is known with high confidence
to belong to individual $a$. Equivalently, ${\cal C}$ can be seen as a set of partial
clusters $c_a$, each including all signatures $s$ for which $(s, a) \in {\cal C}$.

@@

%\glnote{I am not sure we need an explicit algorithm, but adding a few examples would help.}

@@

\subsection{Semi-supervised clustering}
\label{methods:clustering}

The last component of our author disambiguation pipeline is clustering, that is
the process of grouping together, within a block, all signatures from the same
individual (and only those). As for many other works on author disambiguation,
we make use of hierarchical clustering \citep{ward1963hierarchical} for
building clusters of signatures in a bottom-up fashion. The method consists in
iteratively merging together the two most similar clusters until all clusters
are eventually merged together at the top of the hierarchy. Similarity between
clusters is evaluated using either complete, single or average linkage, using
as pseudo-distance metric the probability that $s_1$ and $s_2$ correspond to
distinct authors, as calculated from the custom linkage function $d$.

To form flat clusters out of the hierarchy, one must decide on a maximum
distance threshold above which clusters are considered to correspond to
distinct authors.  Exploiting knowledge from the partial clusters known in
${\cal C}$, we evaluate three cut-off strategies:
\begin{itemize}
\item No cut: all signatures from the same block are assumed to be from the same author;
\item Global cut: the threshold is chosen globally over all blocks, as the one maximizing some score $f({\cal C}, \hat{{\cal C}}_t)$;
\item Block cut: the threshold is chosen locally at each block $b$, as the one maximizing some score $f({\cal C}^b, \hat{{\cal C}}^b_t)$;
\end{itemize}
where $\hat{{\cal C}}_t$ denotes the predicted clusters,
restricted to the signatures in ${\cal C}$, when cutting the hierarchy at threshold $t$, and
where ${\cal C}^b$ is the subset of ${\cal C}$ including only those signatures from block $b$.
